---
title: "Untitled"
output: html_document
---

## Load the Primal data 
```{r}
#install.packages("lpSolveAPI")
library(lpSolveAPI)
lprec <- read.lp("Primal.lp")

```

## Solve the Primal
```{r}
solve(lprec)
get.objective(lprec)
get.variables(lprec)
get.constraints(lprec)
```
***
Shadow prices are the maximum price we can pay for an additional unit of a constraint or resource and it will be calculated by adding 1 to each constraint or variables and calculating the new objective function. Shadow price for a constraint= New objective function - old objective function
Out put for the given below code will show Duals which will give the shadow prices for Constarints and variables (in the order)

***
```{r}
get.sensitivity.rhs(lprec)
```
***

Shadow Prices: 0.00    0.00    0.00   12.00   20.00   60.00    0.00    0.00    0.00   -0.08    0.56 
Dual: 12.00   20.00   60.00
Reduced Costa: 0.00    0.00  -24.00 -40.00    0.00    0.00 -360.00 -120.00    0.00

***

***

Reduced cost is the coefficient of a variable that would need to increase or decrease to make an impact on the optimal solution for maximization or minimization

Given below code gives the Reduced costs and the Range with in which the optimal solution will remain same

***


```{r}
cbind(get.sensitivity.rhs(lprec)) $duals[12:20]
get.sensitivity.rhs(lprec) $duals [12:20]
```

```{r}
get.sensitivity.obj(lprec)
```


## Load the library and the Dual data 
```{r}
lprec2 <- read.lp("Dual.lp")
set.bounds(lprec2,lower = c(-Inf, -Inf),columns= 10:11)

```

## Solve the Dual
```{r}
solve(lprec2)



get.objective(lprec2)
get.variables(lprec2)
get.constraints(lprec2)
```
***
Objective function value is 696000 for the Dual and for the Primal it is 696000

Hence there is strong duality and Primal & Dual agree with each other

***

```{r}
get.sensitivity.rhs(lprec2)

```
```{r}
get.dual.solution(lprec2) [2:12]
get.dual.solution(lprec2) [13:21]

```

***

Hence , based on Objective values , shadow prices and solution for Dual , we can say that Primal and Dual agree with each other.

***

